%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% \input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Austin Wu} \\ \vspace{1pt}
    \small \href{mailto:x@x.com}{\underline{resume@austin-wu.com}} $|$ 
    % \small 408-759-2478 $|$ \href{mailto:x@x.com}{\underline{amw423@cornell.edu}} $|$ 
    \href{https://www.linkedin.com/in/austin--wu/}{\underline{linkedin.com/in/austin--wu/}} $|$
    \href{https://github.com/Austin4705}{\underline{github.com/Austin4705}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
          {Cornell University}{Ithaca, New York}
          {Dual Major: Bachelor of Science in Computer Science and Applied Physics}{Graduation Date: May 2026}
          \resumeItem{Relevant Courseowrk: Math2230, Math2240, CS4999, AEP3200}
          
            \textbf{Awards:} USACO Platinum Competitior,     \textbf{Hackathons Won:} Masseyhacks, Los Altos Hacks, Teenhacks LI
        
    \resumeSubHeadingListEnd
    
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Founding Engineer}{September 2024 -- Present}
      {Deepsilicon (YC24)}{Remote}
      \resumeItemListStart
        \resumeItem{Working on a custom TPU on a FPGA using a quantized 1.5bit architecture to achieve performance speedups.}
        \resumeItem{Implemented Berkeley Hardfloat with for high performance FPU operations}
        \resumeItem{Creating nontrivial optimizations like Chebyshev polynomial approximations for certain algorithms}
        \resumeItem{Set up the FPGA compilation build chain.}
    \resumeItemListEnd\textbf{}
    
    \resumeSubheading
      {Developer}{January 2024 -- Present}
      {Ken Birman Lab of Distributed Systems}{Ithaca, NY}
      \resumeItemListStart
        \resumeItem{Ran internal experimentation using CUDA to optimize caching for large scale matrix multiplication.}
        \resumeItem{Contributed to the Cascade Project by developing a fast vector database using FUSE for RAG.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Researcher}{October 2023 -- Present}
      {Yasuda Lab 2D Quantum Nanomaterials}{Ithaca, NY}
      \resumeItemListStart
        \resumeItem{Developed a full-stack web application using OpenCV, React, Flask, and MongoDB to automate the transfer station machine allowing for exponential speedup of device creation.}
        \resumeItem{Created Non-trivial Computer Vision algorithms for Monolayer Graphene flake detection using color quantization and Machine Learning.}
        \resumeItem{Implemented Complex Control Theory Algorithms such as Model Predictive Control to allow for reliable automatic of the stacking process.}
    \resumeItemListEnd\textbf{}
    
    \resumeSubheading
      {Co Founder and Vice President}{December 2023 -- Present}
      {Quantum Computing Association at Cornell}{Ithaca, NY}
      \resumeItemListStart
        \resumeItem{Contributed to a simulator for Topological Quantum Computing in Python and Rust finds the Isomorphism between the matrix and Topological-Braiding representations of Quantum Computing.}
        \resumeItem{Led development on a building a Neutral Atom Quantum Computer from scratch by building a cheap MOT.}
    \resumeItemListEnd\textbf{}

    \resumeSubheading
      {Researcher}{June 2023 -- September 2023}
      {Independent Collaborator}{Remote}
      \resumeItemListStart
        \resumeItem{Collaborated with Northwestern Professor Seda Memik on a novel in parallel computing architecture with SystemVerilog to create large speedups in computationally intensive workflows. Project was provisionally patented.}
    \resumeItemListEnd\textbf{}

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Cornell Math Modeling Competition Submission} $|$ \emph{C++, Python, LaTeX}}{November 2024 -- November 2024}
          \resumeItemListStart
            \resumeItem{Developed a custom multi-threaded architecture for running heavy simulations in C++ to visualize the spread of Lanturnflies in vineyard populations }
            \resumeItem{Did data analysis in python and wrote up a 40 page paper on the results}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{HeartPal} $|$ \emph{Dart, Flutter, Python, Flask, C/C++, Keras, Git}}{May 2022 -- September 2022}
          \resumeItemListStart
            \resumeItem{Developed a digital stethoscope that connected with a app in Flutter that communicated with a custom LSTM and Hidden Markov Machine Learning model in order to automatically detect irregularities with patients heartbeats.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Python, JavaScript/HTML/CSS, Java, C\#, Rust, Verilog, SystemVerilog} \\
     \textbf{Frameworks}{: CUDA, React/Next, Node.js, Express, MongoDB, Flask, Django, Tailwind} \\
     \textbf{Developer Tools}{: Git, Docker, AWS, Jenkins} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib, OpenCV, PyTorch, Sci-Kit, TensorFlow}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
